---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# drv

<!-- badges: start -->
<!-- badges: end -->

The goal of drv is to provide data from the Ukrainian State Register of Voters

## Installation

You can install the released version of drv from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("drv")
```

or you can install it from Github:

``` r
library(devtools)
install_github("amice13/drv")
```


## Examples

Get all information about Ukrainian regions:

```{r}
library(drv)

head(get_regions())
```
Get all information about organizations of Ukrainian State Register of Voters

```{r}
head(get_drv_entites())
```

Get all election districts

```{r}
get_districts()
```

Get all polling stations in a specified district

```{r}
head(get_polling_stations(12))
```

Get all territories on a specified region:

```{r}
head(get_territories(12))
```
Get all addresses in a specified territories

```{r}
head(get_addresses(12))
```
